Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-06 paper_jasa.tex
small changes, and letter-casing in bib file

\green{Something probably needs to be said about subjects who do multiple tests, what checks are done.} \blue{We do have some data where we notice multiple responses for a lineup by a subject. This happens when subject accidentally use browser's ``back'' button and same data is saved twice. We made sure in the data cleaning process that we do not include more than one response on a lineup by a subject. For this we only keep the very first response.}

@@

\blue{Another critical part is the specific question that the observer needs to answer evaluating the lineup. The question should be more than just asking to find the most different plot. Selecting the appropriate word to describe the pattern we may see when alternative hypothesis is true is important to help the observers understand what pattern they should look for. By delivering an appropriate question may reduce the type III error in an appropriate scenario.}

@@

Experimental subjects in the simulation study came from various level of education, both genders and many different ages. Many subjects had little background in statistics, and were not necessarily aware of statistical plots. Yet the results were good. We expect that visual inference could a useful tool for high school students to learn about randomness as a primer to statistical thinking. A major advantage of visual statisticcal inference is that it is intuitive, as illustrated by the performance of subjects with limited education, and it is may make statistics fun to learn.

>>>>

Note that no participant was shown the same lineup twice.
%\green{Something probably needs to be said about subjects who do multiple tests, what checks are done.} \blue{We do have some data where we notice multiple responses for a lineup by a subject. This happens when subject accidentally use browser's ``back'' button and same data is saved twice. We made sure in the data cleaning process that we do not include more than one response on a lineup by a subject. For this we only keep the very first response.}

@@

\blue{Another critical part is the  question that the observer needs to answer when evaluating the lineup: this question can be lined up with the alternative hypothesis of a classical testing scenario. 
If we are interested in the reason why participants picked a plot as the most different, we need to collect and evaluate this information in the study. This has to be done very carefully, as any suggestions for reasons also lead the observer  what patterns to look out for.}
% By delivering an appropriate question may reduce the type III error in an appropriate scenario.}

@@

Experimental subjects in the simulation study came from various level of education, both genders and many different ages. Many subjects had little background in statistics, and were not necessarily aware of statistical plots. Yet the results were good. We expect that visual inference could a useful tool for high school students to learn about randomness as a primer to statistical thinking. A major advantage of visual statistical inference is that it is intuitive, as illustrated by the performance of subjects with limited education, and it is may make statistics fun to learn.
